---
title: "5008-Group9"
output: html_document
date: "2022-11-22"
---
Name: [Guo, Weiqi]
Student ID: [20925426]\
Name: [He, Jiacheng]
Student ID: [20921341]\
Name: [Wang, Jianhao]
Student ID: [20888886]\
Name: [Zhou, Sitian]
Student ID: [20889385]\
Name: [Feng, Boqiao]
Student ID: [20666501]\
Name: [Zhou, Yuxiang]
Student ID: [20931401]\



```{r}
library(dbplyr)
```

## 1. Function to calculate Discount of cash flow x.
```{r}
Discount <- function(cash_vec,r){
  PV = 0
  for (i in 1:length(cash_vec)){
    PV = PV + cash_vec[i]/((1+r)^(i-1))
  }
  return(PV)
}
```

## 2. Function to calculate the internal rate of return, including IRRs that are complex number.
```{r}
IRR <- function(cash_vec){
  cat("The internal rate k are",round(1/(polyroot(cash_vec))-1,digits = 3), "respectively\n")
  return(round(1/(polyroot(cash_vec))-1,digits = 3))
}
```

## 3. Function to calculate the investment stream.
```{r}
invest_cash <- function(cash_vec,irr){
  c = c()
  for (i in 1:(length(cash_vec)-1)){
    if (i==1){
      c[i] = -cash_vec[i]
    }else{
      c[i] = (1+irr)*c[i-1]-cash_vec[i]
    }
  }
  return(c)
}
```

## 4. Function to calculate the present value of investment stream and output it with the corresponding internal rate k using dataframe.
```{r}
PV_c <- function(cash_vec,market_r){
  PV_cval = c()
  k = IRR(cash_vec)
  for (i in 1:length(k)){
    c = invest_cash(cash_vec,k[i])
    PV_cval[i] = Discount(Re(c),market_r)
  }
  df = data.frame(k,PV_cval)
  print(df)
  return(df)
}
```

## 5. Function to make decision that whether the cash flow is desirable or not.
```{r}
Decision <- function(cash_vec,market_r){
  # From paper we know that even if we have a lot of k, we only need to consider one of them because they will all give the same result.
  # we choose the first k and the corresponding PV of investment cash.
  df = PV_c(cash_vec,market_r)
  k = df$k[1]
  PV_cval = df$PV_cval[1]
  if ((Re(k)-market_r)*PV_cval>0){
    print("Desirable")
  }else{
    print("Undesirable")
  }
}
```

## 6. Function to compare 2 projects.
```{r}
Comparison <- function(x,y,market_r){
  # Get all PV of investment streams and the corresponding k
  x1 = PV_c(x,market_r) 
  y1 = PV_c(y,market_r)
  
  # Find the similar PV_c value of 2 projects
  YmatchIndex = array(0,length(x1$PV_cval))
  min_val = 0.05 # set the tolerance
  # Find the closest PV_c and then compare k
  for (i in 1:length(x1$PV_cval)) {
    YmatchIndex[i] = which.min(abs(y1$PV_cval - x1$PV_cval[i]))
    if (min(abs(y1$PV_cval - x1$PV_cval[i]))<min_val){
      min_val = min(abs(y1$PV_cval - x1$PV_cval[i]))
      target_x = x1$PV_cval[i]
      k_x = x1$k[i]
      target_y = y1$PV_cval[YmatchIndex[i]]
      k_y = y1$k[i]
    }
  }
  # If we dont find the similar PV of investment stream(PV_c), we compare the projects using NPV directly.
  if (min_val == 0.05){
    print("The projects don't have similar PV of investment streams, so we calculate PV of cash flow to compare them directly.")
    cat("The PVs of cash flow are",Discount(x,market_r),Discount(y,market_r),"respectively.\n")
    if(Discount(x,market_r)>Discount(y,market_r)){
      print("Choose X")
    }else{
      print("Choose Y")
    }
  }
  # If we find the similar investment streams, we compare them using the corresponding k.
  else{
    cat("The equal or similar PV of investment streams are",target_x,target_y,"respectively and the corresponding k are",k_x,k_y,"\n")
    # If PV_c is net borrowing, we choose smaller internal rate.
    if (target_x & target_y <0){
      if (Re(k_x)< Re(k_y)){
        print("Choose X")
      }else{
        print("Choose Y")
      }
    }
    # If PV_c is net investing, we choose larger internal rate.
    else{
      if (Re(k_x)>Re(k_y)){
        print("Choose X")
      }else{
        print("Choose Y")
      }
    }
  }
}

```

## Our examples
### 1.
```{r}
r = 0.1
x1 = c(-1,6,-11,6)
IRR(x1)
invest_cash(x1,0)
Decision(x1,r)

x2 = c(-1,3,-2.5)
IRR(x2)
Decision(x2,r)
Discount(x2,r)
```
### 2.
```{r}
cf = c(500, -1000, 0, 250, 250, 250)
r=0.1
Decision(cf,r)
Discount(cf,r)
```
### 3.
```{r}
# Compare 2 projects
r = 0.1
x1 = c(-20,14,10,6,2,-2)
y1 = c(-20,-6,1.1,8.2,15.3,22.4)
Comparison(x1,y1,r)

x2 = c(-1,5,-6)
y2 = c(-1,4,-4)
Comparison(x2,y2,r)
```
### 4.
```{r}
r=0.06
cf1 <- c(-24,-4.8,-9.6,14.40,-4.8)
cf2 <- c(-24,18.46,0,24,-18.46)
cf3 <- c(-24,108,48,72,-60)
a=IRR(cf1)
b=IRR(cf2)
c=IRR(cf3)
Decision(cf1,r)
Decision(cf2,r)
Decision(cf3,r)
Discount(cf1,r)
Discount(cf2,r)
Discount(cf3,r)
```
